---
title: "R Notebook"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Base plotting system

Including two packages: graphics and grDevices.

Process of making plot:   
**1.**  Initial a new plot. Using the "plot(x,y)" or "hist(x)".  
**2.**  Annotate the existing plot.  
Note: Using “?par” to know the parameters.  "Par()" is the function that set
parameters for all the plots in the R session and could over-ride the local 
parameters.(parameters such as "mfrow", "mfcol")

#### 1. Ways to initial the plot.

```{r}
hist(airquality$Ozone)
with(airquality, plot(Wind, Ozone))
airquality <- transform(airquality, Month = factor(Month))
boxplot(Ozone ~ Month, airquality, xlab = "Month", ylab = "Ozone (ppb)")
par("lty")
par("col")
par("mfrow")
```
#### 2. Annotate the existing plot. 
+  Base ploting functions:
  plot, lines, points, text(add text labele), title, mtext(add text to margin), axis(add axis ticks).

```{r}
with(airquality, plot(Wind, Ozone))
title(main = "Ozone and Wind in NYC")
with(subset(airquality, Month == 5 ), points(Wind, Ozone, col = "blue"))
with(subset(airquality, Month != 5), points(Wind, Ozone, col = "Red"))
legend("topright", pch = 1, col = c("blue", "red"), legend = c("May", "Others"))

```

```{r}
with(airquality, plot(Wind, Ozone, main = "Ozone and Wind in NYC"), pch = 20)
model <- lm(Ozone ~ Wind, airquality)
abline(model, lwd=2)
```

```{r}
par(mfrow = c(1, 3), oma= c(0,0,2,0))
with(airquality, {
  plot(Wind, Ozone, main = "Ozne and Wind")
  plot(Solar.R, Ozone, main = "Ozone and Solar Radiation")
  plot(Temp, Ozone, main = "Ozone and Temprature")
  mtext("Ozone and Weather in NYC", outer = T) # Why doesn't work? Because the default oma is 0.
})
```

#### 3. Plot device.
A graphic device is where you can make a picture appears, fox example, screen, pdf, svg.
```{r}
pdf()
dev.off()
```


